Evaluating the Influence of Education on Current Unemployment Trends

### 2024-03-29 paper/paper.qmd
updated references and paper

# Use modelsummary to create the table
modelsummary::modelsummary(
  list(
    "Baseline Model for Youth Unemployment" = model
  ),
  coef_rename = custom_coef_names,
  stars = TRUE,
  fmt = 2,
)
```

@@

## First discussion point

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

## Third discussion point

>>>>

# Use modelsummary to create the table
modelsummary::modelsummary(
  list(
    "Baseline Model for Youth Unemployment" = model
  ),
  coef_rename = custom_coef_names,
  stars = FALSE,
  fmt = 2,
)
```

@@

Given the results, it is important for us to discuss why we are seeing such results, and what they actually mean moving forward.

## What we learn from these results

## Why are we seeing these results

## What could this entail for the future
